\experienceheader
    % {ML Engineer}
    {Data Scientist}
    {, Immigration, Refugees and Citizenship Canada}
    {Oct 2022 - Present}
    {Advanced Analytics Solutions Center}
\vspace{-0.3em}
\begin{zitemize}\itemsep 2pt
    \item Lead engineer for the Temporary Resident Visa, the team's highest-throughput ML platform, \textbf{processing \textasciitilde150K files weekly} through production PySpark, PyArrow, and Pandas pipelines over Parquet storage with real-time decision support. 
    \item Redesigned a high-risk classification model with novel feature engineering, \textbf{reducing false approvals by 54\%}.
    \item Optimized a production PySpark pipeline end-to-end, \textbf{reducing runtime 60\% (8h to 3h)} through Spark job refactoring, deduplication, and compute environment tuning.
    \item Architected a 40+ SQL star schema feature layer, transforming raw operational data into model-ready datasets, powering a \textbf{30+ bin classification system} used by hundreds of IRCC officers.
    \item Coordinated the full ML deployment pipeline: Docker containers, published to AWS ECR, ECS via CDK, with PR-tracked versions in Azure DevOps and structured logging for monitoring.
    \item Expanded platform coverage to new applicant categories: cross-model integrations and initiatives like FIFA 2026.
\end{zitemize}

\experienceheader
    {Data Analyst}
    {, Immigration, Refugees and Citizenship Canada}
    {Dec 2020 - Oct 2022}
    {Anti Racism Task Force}
\vspace{-0.3em}
\begin{zitemize}\itemsep 2pt
    \item Technical lead for a cross-departmental team
    \item Built R-Shiny dashboards and performed ad-hoc analyses on an 8,000 employee dataset for equity gaps.
    \item Designed a department-wide survey; presented findings to DG-level executives to inform policy decisions.
\end{zitemize}

\experienceheader
    {Research Assistant - Capstone}
    {, CAE Inc.}
    {Oct 2022 - Apr 2023}
    {}
\begin{zitemize}\itemsep 2pt
    \item Built a forecasting pipeline with model selection to predict demand for thousands of aviation components.
    \item Designed an inventory policy balancing demand, lead times, and service-level targets to reduce inventory costs.
\end{zitemize}
% \vspace{0.3em}

\experienceheader
    {Research Assistant}
    {, University of Ottawa}
    {May 2019 - Aug 2019}
    {}
\begin{zitemize}\itemsep 2pt
    \item Developed a mixed-integer scheduling model with 100+ constraints to generate a year-long timetable, cutting planning time from weeks to hours and improving fairness and utilization.
    \item Built a web app with React and Django to let staff run and evaluate scheduling scenarios.
\end{zitemize}