\subsection{{Infinite DnD \hfill July 2025 --- Present}}
\subtext{Personal}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Developing an LLM-agent system using open-source models to run Dungeons \& Dragons campaigns from user-defined configurations; supports fully automated play or mixed human/agent interaction.
    \item Architected modular LLM agents with scoped world knowledge to improve response accuracy and separation of concerns.
    \item Implemented persistent world state, enabling agent to create lasting consequences (quests, NPCs, events).
    \item Designed and implemented a React frontend to present narrative, visualize world state and agent logs, and capture user input.
\end{zitemize}
\vspace{0.75em}

\subsection{{Academic Consulting Project \hfill Oct 2022 --- Apr 2023}}
\subtext{CAE Inc. \hfill Montreal, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Developed a time-series forecasting pipeline to predict demand for thousands of aviation components, with automatic algorithm selection based on component characteristics and historical performance.
    \item Designed an inventory management policy balancing forecast uncertainty, lead times, and service-level targets to reduce stockouts and holding costs.
    \item Communicated results in an executive report, translating technical findings into actionable procurement and operations recommendations.
\end{zitemize}
\vspace{0.75em}

\subsection{{Workload Allocation \hfill May 2019 --- Feb 2020}}
\subtext{Telfer School of Management \hfill Ottawa, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Designed and solved a mixed-integer optimization model to generate a full-year teaching schedule, decreasing planning time from weeks to hours and improving constraint satisfaction.
    \item Implemented a production web app (React frontend, Django backend) enabling staff to run scheduling scenarios.
    \item Enhanced the model by adding soft constraints for instructor preferences and room capacities, improving fairness and utilization.
\end{zitemize}