\subsection{{Infinite DnD \hfill July 2025 --- Present}}
\subtext{Personal Project (LLM Agents / Data Infrastructure)}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Engineered modular open-source LLM agent system (Python) separating narrative generation, rule enforcement, and world simulation via scoped knowledge modules.
    \item Implemented persistent, normalized world state (entities, attributes, events) enabling long-horizon consistency and queryable session analytics.
    \item Built React + TypeScript interface to stream agent outputs, visualize state diffs, and surface structured logs; accelerated iteration cycle by <X%>.
    \item Added structured JSON logging, session tracing, and evaluation harness tracking latency, token usage, and narrative quality across model variants.
    \item Containerized services (agents API, state store, frontend) with Docker; designed for Azure deployment (env config, reproducible dev workflow, CI/CD ready).
\end{zitemize}
\vspace{0.75em}

\subsection{{Academic Consulting Project \hfill Oct 2022 --- Apr 2023}}
\subtext{CAE Inc. \hfill Montreal, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Developed a time-series forecasting pipeline to predict demand for thousands of aviation components, with automatic algorithm selection based on component characteristics and historical performance.
    \item Designed an inventory management policy balancing forecast uncertainty, lead times, and service-level targets to reduce stockouts and holding costs.
    \item Communicated results in an executive report, translating technical findings into actionable procurement and operations recommendations.
\end{zitemize}
\vspace{0.75em}

\subsection{{Workload Allocation \hfill May 2019 --- Feb 2020}}
\subtext{Telfer School of Management \hfill Ottawa, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Designed and solved a mixed-integer optimization model to generate a full-year teaching schedule, decreasing planning time from weeks to hours and improving constraint satisfaction.
    \item Implemented a production web app (React frontend, Django backend) enabling staff to run scheduling scenarios.
    \item Enhanced the model by adding soft constraints for instructor preferences and room capacities, improving fairness and utilization.
\end{zitemize}