\subsection{{Data Scientist, Advanced Analytics Solutions Center \hfill Oct 2022 --- Present (Full-time)}}
\subtext{Immigration, Refugees and Citizenship Canada \hfill Remote / Ottawa, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Lead data science for the Temporary Resident Visa predictive platform, processing 150{,}000+ files weekly to prioritize case reviews and optimize officer workload allocation—directly supporting operational decisions for hundreds of IRCC officers.
    \item Maintain and enhance production-grade 30+ bin classification system consolidating 40+ SQL views; designed ML pipeline components to automate model updates, enabling real-time risk stratification while maintaining decision quality.
    \item Contributed to migrating SPSS monolith to production PySpark pipeline; refactored 10{,}000 LOC of Python, improved end-to-end performance by 15\%, and supported implementation of CI/CD practices for ML model deployment.
    \item Partner with Software Engineers, Product Managers, and Business Analysts to translate business requirements into ML solutions; deliver 10+ weekly operational reports and ad-hoc analyses driving KPI-based decision-making.
    \item Own data contracts with downstream systems, ensuring data quality and reliability for mission-critical immigration processing workflows.
\end{zitemize}
\vspace{0.75em}

\subsection{{Data Analyst, Anti-Racism Task Force \hfill Dec 2020 --- Oct 2022 (Full-time)}}
\subtext{Immigration, Refugees and Citizenship Canada \hfill Ottawa, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Served as technical lead for departmental Anti-Racism Task Force; conducted statistical analyses on HR data and department-wide survey, uncovering systemic hiring inequities that informed executive policy decisions.
    \item Prepared executive-ready briefings and data visualizations, translating complex statistical findings into compelling narratives that secured leadership buy-in and drove policy changes impacting thousands of employees.
\end{zitemize}
\vspace{0.75em}

\subsection{{\textbf{Professional Research} \hfill May 2019 --- Aug 2023}}
\vspace{0.2em}

\textbf{Ottawa Hospital Research Institute} \hfill Feb 2020 --- Aug 2020 (Full-time)
\begin{zitemize}
    \vspace{-0.5em}
    \item Applied operations research and statistical modeling to healthcare scheduling; designed optimization models reducing wait times and improving capacity utilization.
\end{zitemize}

\vspace{0.5em}
\textbf{McGill University} \hfill Mar 2023 --- Aug 2023 (Part-time)
\begin{zitemize}
    \vspace{-0.5em}
    \item Built and deployed production web applications (AWS/GCP) for animal-accident tracking; implemented facility-location optimization model for wildlife-crossing placement.
\end{zitemize}

\vspace{0.5em}
\textbf{University of Ottawa} \hfill May 2019 (Part-time)
\begin{zitemize}
    \vspace{-0.5em}
    \item Developed Markov Decision Process model for surgery scheduling; conducted simulation experiments to reduce wait times for high-priority patients.
\end{zitemize}

