\subsection{{Data Scientist, Advanced Analytics Solutions Center \hfill Oct 2022 --- Present}}
\subtext{Immigration, Refugees and Citizenship Canada \hfill Montreal, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Work in a cross-functional team with Software Engineers, Product Managers, and Business Analysts to build data-driven decision-support tools used in daily operations.
    \item Lead engineer for the Temporary Resident Visa predictive platform, the highest-volume file classification system on our team, scoring approximately 200{,}000 files per week.
    \item Helped migrate an SPSS monolith into a production PySpark pipeline; refactored the Python codebase (removed approximately 10{,}000 LOC) and improved end-to-end performance by about 15\% (so far).
    \item Design and maintain a 30+ bin classification system that consolidates 40+ SQL views and powers daily decisions for hundreds of IRCC officers.
    \item Own 10+ weekly operational reports, downstream data contracts, and ad-hoc analyses that inform business decisions and operational KPIs.
\end{zitemize}
\vspace{0.75em}

\subsection{{Research Assistant \hfill Mar 2023 --- Aug 2023}}
\subtext{McGill University \hfill Montreal, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Built and deployed two public-facing sites (AWS/GCP) for animal-accident management and glyphosate research.
    \item Animal-accident site tracks accidents and optimizes wildlife-crossing placement via a facility-location model.
\end{zitemize}
\vspace{0.75em}

\subsection{{Data Analyst, Anti-Racism Task Force \hfill Dec 2020 --- Oct 2022}}
\subtext{Immigration, Refugees and Citizenship Canada \hfill Ottawa, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Served as a technical lead for an Anti-Racism Task Force team; set analytics priorities and drove deliverables.
    \item Ran a department survey and HR analyses that uncovered hiring inequities and informed policy decisions.
    \item Prepared executive-ready briefings, converting analysis into actionable insights that secured leadership buy-in.
\end{zitemize}
\vspace{0.75em}

% \subsection{Project Officer, Employee Experience Team \hfill Oct 2020 --- Dec 2020}
% \subtext{Immigration, Refugees and Citizenship Canada \hfill Ottawa, Canada}
% \begin{zitemize}
% \setlength\itemsep{0.4em}
% \item Streamlined the process of connecting students to recruiters by designing a database, a query UI, and a data entry form, reducing hiring managers' workload.
% \end{zitemize}

\subsection{{Research Assistant \hfill Feb 2020 --- Aug 2020}}
\subtext{Ottawa Hospital Research Institute \hfill Ottawa, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Analyzed patient-level and scheduling datasets to prepare inputs for optimization and simulation models.
    \item Applied operations research techniques to improve patient scheduling, block scheduling, and capacity planning.
\end{zitemize}
\vspace{0.75em}

\subsection{{Research Assistant \hfill May 2019}}
\subtext{University of Ottawa \hfill Ottawa, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Applied Markov Decision Process model for surgery scheduling, to reduce wait times for high-priority patients.
    \item Conducted simulation experiments to evaluate hypotheses and support a master's student thesis.
\end{zitemize}

