\subsection{{Infinite DnD \hfill July 2025 --- Present}}
\subtext{Personal}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Working on an LLM agent based system using open-source models to run Dungeons \& Dragons campaigns from user-defined configurations; supports fully automated play or mixed human/agent interaction.
    \item Architected modular LLM agents for distinct responsibilities with scoped world knowledge to improve responses.
    \item Contains a persistent world state allowing agents to create lasting consequences (quests, NPC state, world events)
    \item Designed a React front-end to present narrative, visualize world state, agent logs, and enable user inputs.
\end{zitemize}
\vspace{0.75em}

\subsection{{Academic Consulting Project \hfill Oct 2022 --- Apr 2023}}
\subtext{CAE Inc. \hfill Montreal, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Developed an automated time-series forecasting pipeline to predict demand for thousands of aviation components; automatic algorithm selection based on component characteristics and historical performance.
    \item Designed an inventory management policy that balanced forecast uncertainty, lead times, and service-level targets.
    \item Communicated results to stakeholders through an executive report, translating technical findings into actionable recommendations for procurement and operations.
\end{zitemize}
\vspace{0.75em}

\subsection{{Workload Allocation \hfill May 2019 --- Feb 2020}}
\subtext{Telfer School of Management \hfill Ottawa, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Designed and solved a mixed-integer optimization model to generate a full-year teaching schedule; decreased planning time from weeks to hours and increased constraint satisfaction.
    \item Implemented a production web application (React frontend, Django backend) to enable staff to run rescheduling scenarios and capture instructor preferences.
    \item Enhanced the model to incorporate soft constraints for instructor preferences and room capacities, improving perceived fairness and utilization.
\end{zitemize}