% Original projects section (backup)
\subsection{{Infinite DnD \hfill July 2025 --- Present}}
\subtext{Personal}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Uses open-source LLMs to generate automatic Dungeons and Dragons campaigns based on user defined configuration. With the option of either automatic play, or user-defined actions.
    \item Various LLM agents for different tasks with different world information available to each (e.g., DM world-building, character agents, DM combat, NPC characters, etc) 
    \item Persistent world state with agents having the ability to affect the world, quests, and NPCs.
    \item React based front-end to display narrative, world states, user interactions, and LLM logs.
\end{zitemize}
\vspace{0.75em}

\subsection{{Academic Consulting Project \hfill Oct 2022 --- Apr 2023}}
\subtext{CAE Inc. \hfill Montreal, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Built a time-series forecasting model to predict demand for thousands of aviation components, with automatic algorithm selection based on component characteristics.
    \item Designed an inventory management policy based on forecasted demand, lead times, and service-level targets.
    \item Prepared an executive report summarizing findings and recommendations for CAE Inc.
\end{zitemize}
\vspace{0.75em}

\subsection{{Workload Allocation \hfill May 2019 --- Feb 2020}}
\subtext{Telfer School of Management \hfill Ottawa, Canada}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Developed a mathematical optimization model to create a full-year teaching schedule, reducing planning time from weeks to hours.
    \item Implemented a user-friendly web interface (React+Django) to support deployment and adoption by users.
    \item In addition to satisfying basic constraints, the model considered instructor preferences and classroom space.
\end{zitemize}
